### 2017-06-18 paper.tex
Remove salt and pepper (excess) words

Despite the proven success of open-source and collaboratively developed lesson plans,
it is surprisingly uncommon in the traditional accademic setting.
Each year, thousands of university lecturers teach subjects ranging from first year biology,
to graduate-level courses in Indian film.
Some might use a common textbook written by a single author or two,
but besides that lecturers develop and improve their course materials in isolation.
It is staggering to think how many wheels are being re-invented,
how much valuable time has been wasted,
and ultimately how the progress of tertiary education has been held back by
the lack of community collaboration and sharing in this process.
This problem obviously extends beyond the university sector,
but it is curious that it is endemic in tertiary education,
given that research depends so critically on collaboration and sharing,
and that most researchers complain about how much time teaching takes away from research.

The authors collectively have experience with community-developed lesson plans
in the context of research computing in the sciences and humanities.
They primarily draw on their experiences with pedagogical organizations such as
Software Carpentry and Programming Historian.
Software Carpentry was founded in 1998 to teach scientists basic computing skills,
and has since spawned two sibling organizations called Data Carpentry and Library Carpentry.
Programming Historian was founded in 2008,
and has evolved into a collaboratively-edited site providing lessons to humanists.
These organizations have been successful in adapting open source development methods
to lesson development and maintenance.
Their guiding principles are that lessons should be:

@@

Open education projects satisfy the first criterion by definition,
but very few projects satisfy the second.
While their lessons might occasionally be updated by a small author group,
as happens when a new edition of a book is edited and published,
this is not the same as continuous improvement by a large community of contributors.
The ten simple rules that follow summarize what we have learned about doing that
as maintainers, editors, and reviewers of lessons used by tens of thousands of people.

@@

Doing this shifts the instructor's burden from writing to finding and synthesizing,
both of which are easier if lessons have been designed by people with a shared world-view (Rule~4),
and if lessons clearly signal what they cover (Rule~1).
In particular,
if lessons reference specific points in the model curriculum guidelines promulgated by many professional societies,
it can be much easier for people to find them and integrate them.

@@

Decades of pedagogical research has yielded many insights into
how best to build and deliver lessons \cite{hlw}.
Unfortunately,
since most college and university faculty have little or no training in education,
this knowledge and expertise is rarely transferred into classroom practice.

@@

An example of how to teach these practices is Software Carpentry's instructor training program.
First offered in 2012,
is now a two-day course delivered both in-person and online
\cite{lessons-learned,instructor-training,how-to-teach-programming}.
Not only does it teach good pedagogical practices,
it serves and an onboarding process to get everyone on the same page
regarding who lessons are for,
how they are delivered,
and how they are maintained.

@@

Tools can help,
especially if they allow proposed changes to be viewed and discussed
prior to their incorporation/merger into the lessons
(in open source software development this is known as ``pre-merge review'').
Providing a gentle on-ramp for new contributors is essential,
but some tools come with a considerable up-front learning curve.
Housing lessons on GitHub with changes suggested via pull requests is 
ideal for pre-merge review, for instance,
but it requires contributors to know how to use Git,
which has a notoriously steep learning curve \cite{git-survey}.
Allowing people to edit a Google Doc or Wiki-based editing does not offer pre-merge review,
but the low barrier to entry can help get conversations started.

@@

If lessons are being released regularly,
automate the process
with a shell script or something similar.
Old versions of lessons should be archived in a discoverable location for reference.

@@

Pre- and post-class surveys can be used to discover larger macro-scale issues.
These issues often relate to the fact that it can be difficult for lesson developers
to fully understand the frame of reference of their audience.
For instance, a lesson might inadvertently assume prior knowledge that many learners don't have,
which is information that can be collected in a survey.
If possible, it's a good idea to conduct the post-class survey 30--60 days after the fact.
This allows people time to reflect,
meaning they are more likely to give accurate feedback on what they learned
rather than how entertained they were.

@@

No single lesson can be right for every learner.
Two people with no prior knowledge of a specific subject
may still be able to move at very different speeds
because of different levels of general background knowledge.
Similarly,
lessons on ecology for learners in Utah and Florida
will probably be more relatable if they use different examples.
Equally,
no lesson development community can serve all purposes.
Some groups may prioritize rapid evolution,
while others may prefer a ``measure twice, cut once'' approach.

If there are several complementary ways to explain something,
or several points of views that can cohabit respectfully,
it may be possible to present them side by side.
There are actually good pedagogical reasons to do this
even if contributors \emph{don't} disagree:
weighing alternatives fosters higher-order thinking,
and as Caulfield has written,
the most popular online question and answer sites
are successful in part because they present a chorus of explanations
geared at different levels and needs
rather than a single one \cite{choral-explanations}.

@@

Forking rarely happens in practice.
When it does,
it is important to remember that we all share the same vision of better lessons, built together.

>>>>

Despite the proven success of open-source and collaboratively developed lesson plans,
it is uncommon in the traditional accademic setting.
Each year, thousands of university lecturers teach subjects ranging from first year biology,
to graduate-level courses in Indian film.
Some use a common textbook written by a single author or two,
but besides that lecturers develop and improve their course materials in isolation.
It is staggering to think how many wheels are being re-invented,
how much valuable time has been wasted,
and ultimately how the progress of post-secondary education has been held back by
the lack of community collaboration and sharing in this process.
This problem obviously extends beyond the university sector,
but it is curious that it is endemic in post-secondary education,
given that research depends so critically on collaboration and sharing,
and that most researchers complain about how much time teaching takes away from research.

The authors collectively have experience with community-developed lesson plans
in the context of research computing in the sciences and humanities.
They primarily draw on their experiences with pedagogical organizations such as
Software Carpentry and Programming Historian.
Software Carpentry was founded in 1998 to teach scientists basic computing skills,
and has since spawned two sibling organizations called Data Carpentry and Library Carpentry.
Programming Historian was founded in 2008,
and has evolved into a collaboratively-edited site providing lessons to humanities scholars.
These organizations have been successful in adapting open source development methods
to lesson development and maintenance.
Their guiding principles are that lessons should be:

@@

Open education projects satisfy the first criterion by definition,
but few projects satisfy the second.
While their lessons are occasionally updated by a small author group,
as happens when a new edition of a book is edited and published,
this is not the same as continuous improvement by a large community of contributors.
The ten simple rules that follow summarize what we have learned about doing that
as maintainers, editors, and reviewers of lessons used by tens of thousands of people.

@@

Doing this shifts the instructor's burden from writing to finding and synthesizing,
both of which are easier if lessons have been designed by people with a shared world-view (Rule~4),
and if lessons clearly signal what they cover (Rule~1).
In particular,
if lessons reference specific points in the model curriculum guidelines promulgated by professional societies,
it can be much easier for people to find them and integrate them.

@@

Decades of pedagogical research has yielded insights into
how best to build and deliver lessons \cite{hlw}.
Unfortunately,
since most college and university faculty have little or no training in education,
this knowledge and expertise is rarely transferred into classroom practice.

@@

An example of how to teach these practices is Software Carpentry's instructor training program.
First offered in 2012,
is now a two-day course delivered both in-person and online
\cite{lessons-learned,instructor-training,how-to-teach-programming}.
Not only does it teach good pedagogical practices,
it serves and an introductory process to get everyone on the same page
regarding who lessons are for,
how they are delivered,
and how they are maintained.

@@

Tools can help,
especially if they allow proposed changes to be viewed and discussed
prior to their incorporation into the lessons
(in open source software development this is known as ``pre-merge review'').
Providing a gentle on-ramp for new contributors is essential,
but some tools come with a considerable up-front learning curve.
Housing lessons on GitHub (a web-based version control system)
with changes suggested via pull requests (requests to incorporate changes) is 
ideal for pre-merge review, for instance,
but it requires contributors to know how to use Git,
which has a notoriously steep learning curve \cite{git-survey}.
Allowing people to edit a Google Doc or Wiki-based editing does not offer pre-merge review,
but the low barrier to entry can help get conversations started.

@@

If lessons are being released regularly,
automate the process.
Old versions of lessons should be archived in a discoverable location for reference.

@@

Pre- and post-class surveys can be used to discover larger macro-scale issues.
These issues often relate to the fact that it can be difficult for lesson developers
to fully understand the frame of reference of their audience.
For instance, a lesson might inadvertently assume prior knowledge that learners don't have,
which is information that can be collected in a survey.
If possible, it's a good idea to conduct the post-class survey 30--60 days after the fact.
This allows people time to reflect,
meaning they are more likely to give accurate feedback on what they learned
rather than how entertained they were.

@@

No single lesson can be right for every learner.
Two people with no prior knowledge of a specific subject
may still be able to move at different speeds
because of different levels of general background knowledge.
Similarly,
lessons on ecology for learners in Utah and Florida
will probably be more relatable if they use different examples.
Equally,
no lesson development community can serve all purposes.
Some groups may prioritize rapid evolution,
while others may prefer a ``measure twice, cut once'' approach.

If there are complementary ways to explain something,
or points of view that can cohabit respectfully,
it may be possible to present them side by side.
There are actually good pedagogical reasons to do this
even if contributors \emph{don't} disagree:
weighing alternatives fosters higher-order thinking,
and as Caulfield has written,
the most popular online question and answer sites
are successful in part because they present a chorus of explanations
geared at different levels and needs
rather than a single one \cite{choral-explanations}.

@@

These splits rarely happen in practice.
When they do,
it is important to remember that we all share the same vision of better lessons, built together.
